### 2019-07-07 2-Chapters/Conclusion/conclusion.tex
Citations de Kaamelott pour le début de la thèse… ??

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:2}}.}

We started by presenting the multi-armed bandit model, with a finite number of arms and real-valued rewards.
Our focus is on one-dimensional exponential families of distributions, and on stochastic and stationary problems.
The notations used in the manuscript were introduced by showcasing an interactive demonstration.
% \footnote{See \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}}.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:3}}.}

Then we presented our Python library SMPyBandits \cite{SMPyBanditsJMLR,SMPyBandits}, by detailing
its purpose and qualities, its organization, and an overview of its usage.
%
This library allows any researcher to easily implement numerical simulations of stochastic or piece-wise stochastic problems of single- or multi-players multi-armed bandits.
SMPyBandits is distributed on GitHub and Pypi freely, under an open-source license (MIT License), and it is extensively documented (at \href{https://SMPyBandits.GitHub.io}{\texttt{SMPyBandits.GitHub.io}}).
% Our library allows any researcher to easily run numerical simulations of different kinds of multi-armed bandit problems, requiring only a small knowledge of Python thanks to its documentation, its well-designed API, and many examples of simulation scripts and configuration files included.

@@

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:25}}.}
%
This first part ends by presenting one of our first contributions \cite{Besson2018WCNC}.
We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing her favorite algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, a third solution for a practitioner can be to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We proposed an extension of the \ExpFour{} algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:4}}.}

This chapter started the second part of the manuscript, Part~\ref{part:MABIOT}, and presents three main contributions.

First in Section~\ref{sec:4:firstModel}, we proposed an evaluation of the performance of applying MAB learning algorithms in IoT networks,
with a focus on the convergence of algorithms, in terms of successful transmission rates.
We restrict to the case of a protocol slotted in both time and frequency, and we assume a certain clock pre-agreement and time synchronisation between devices and the base station.
We studied the behavior of the network when the proportion of intelligent dynamic devices changes.
Concretely, increasing this probability allows to insert more devices in the same network, while maintaining a good Quality of Service.
Another way of viewing this result is the opposite point-of-view: if the number of devices remains constant, increasing the successful transmission rate directly improves the network QoS.
%  as the base station receives more accurately the data sent by the end-devices since less transmissions failed.
We show that \UCB{} and Thompson sampling algorithms both have near-optimal performance, even when their underlying \iid{} assumption (see Chapter~\ref{chapter:2}) is violated by the presence of many ``intelligent'' end-devices which all follow a random activation process.
%
This was both surprising and encouraging, as it shows that applying bandit algorithms tailored for a stochastic model is still useful in broader settings.
The fully \emph{decentralized} application of classic stochastic MAB algorithms are almost as efficient as the best possible centralized policy in this setting, after a short learning period, even though the dynamic devices \emph{cannot} communicate with each other, and \emph{do not} know the system parameters.

@@

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:5}}.}

@@

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:6}}.}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Part~\ref{part:Introduction}}.}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter~\ref{chapter:4}}.}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter~\ref{chapter:5}}.}

The study on multi-players bandits suggests several further research directions.
First, one could want to investigate the notion of \emph{optimal algorithms} in the decentralized multi-players model with sensing information.
So far we provided the first matching upper and lower bound on the expected number of sub-optimal arms selections, which suggests some form of (asymptotic) optimality.
However, sub-optimal draws turn out not be the dominant terms in the regret, both in our upper bounds and in practice, thus a promising future work is to identify some notion of \emph{minimal number of collisions}, like a recent work \cite{wang2019distributed} studied the minimal amount of communication needed to achieve logarithmic regret, in a similar model that authorizes direct communications between players.
% Similarly to what was done very recently in \cite{wang2019distributed} for the communications between players who collaborate with each other, it would be interesting to characterize the number of collisions needed to achieve logarithmic regret.

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter~\ref{chapter:6}}.}

We believe that our new proof technique could be used to analyze \GLRklUCB{} under less stringent assumptions than the one made in this chapter (and in previous works), that would require only a few ``meaningful'' changes to be detected.
This promising research direction is left for future work,  but the hope is that the regret would be expressed in term of this number of meaningful changes instead of the number of break-points $\Upsilon_T$.
We shall also investigate whether actively adaptive approaches can attain a $\cO(\sqrt{\Upsilon_T T})$ regret upper-bound without the knowledge of $\Upsilon_T$.
We also believe that combining change-point \emph{localization} with an efficient change-point detection algorithm, such as \GLRklUCB, could lead to an interesting class of more efficient algorithms, as suggested by \cite{Maillard2018GLR}.

>>>>

% ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter~\ref{chapter:2}}.}

We started in Chapter~\ref{chapter:2} by presenting the multi-armed bandit model, with a finite number of arms and real-valued rewards.
Our focus is on one-dimensional exponential families of distributions, and on stochastic and stationary problems.
The notations used in the manuscript were introduced by showcasing an interactive demonstration.
% \footnote{See \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}}.

% ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter~\ref{chapter:3}}.}

Then we presented in Chapter~\ref{chapter:3} our Python library SMPyBandits \cite{SMPyBanditsJMLR,SMPyBandits}, by detailing
its purpose and qualities, its organization, and an overview of its usage.
%
This library allows any researcher to easily implement numerical simulations of stochastic or piece-wise stochastic problems of single- or multi-players multi-armed bandits.
SMPyBandits is distributed on GitHub and Pypi freely, under an open-source license (MIT License), and it is extensively documented (at \href{https://SMPyBandits.GitHub.io}{\texttt{SMPyBandits.GitHub.io}}).
% Our library allows any researcher to easily run numerical simulations of different kinds of multi-armed bandit problems, requiring only a small knowledge of Python thanks to its documentation, its well-designed API, and many examples of simulation scripts and configuration files included.

@@

% ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter~\ref{chapter:25}}.}
%
This first part ends by presenting one of our first contributions \cite{Besson2018WCNC}, in Chapter~\ref{chapter:25}.
We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing her favorite algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, a third solution for a practitioner can be to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We proposed an extension of the \ExpFour{} algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.

% ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter~\ref{chapter:4}}.}

Chapter~\ref{chapter:4} started the second part of the manuscript, Part~\ref{part:MABIOT}, and presents three main contributions.
%
First in Section~\ref{sec:4:firstModel}, we proposed an evaluation of the performance of applying MAB learning algorithms in IoT networks,
with a focus on the convergence of algorithms, in terms of successful transmission rates.
We restrict to the case of a protocol slotted in both time and frequency, and we assume a certain clock pre-agreement and time synchronisation between devices and the base station.
We studied the behavior of the network when the proportion of intelligent dynamic devices changes.
Concretely, increasing this probability allows to insert more devices in the same network, while maintaining a good Quality of Service.
Another way of viewing this result is the opposite point-of-view: if the number of devices remains constant, increasing the successful transmission rate directly improves the network QoS.
%  as the base station receives more accurately the data sent by the end-devices since less transmissions failed.
We show that \UCB{} and Thompson sampling algorithms both have near-optimal performance, even when their underlying \iid{} assumption (see Chapter~\ref{chapter:2}) is violated by the presence of many ``intelligent'' end-devices which all follow a random activation process.
%
This was both surprising and encouraging, as it shows that applying bandit algorithms tailored for a stochastic model is still useful in broader settings.
The fully \emph{decentralized} application of classic stochastic MAB algorithms are almost as efficient as the best possible centralized policy in this setting, after a short learning period, even though the dynamic devices \emph{cannot} communicate with each other, and \emph{do not} know the system parameters.

@@

% ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter~\ref{chapter:5}}.}

@@

% ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter~\ref{chapter:6}}.}

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Part~\ref{part:Introduction}}.}

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Chapter~\ref{chapter:4}}.}

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Chapter~\ref{chapter:5}}.}

The study on multi-players bandits in Chapter~\ref{chapter:5} suggests several further research directions.
First, one could want to investigate the notion of \emph{optimal algorithms} in the decentralized multi-players model with sensing information.
So far we provided the first matching upper and lower bound on the expected number of sub-optimal arms selections, which suggests some form of (asymptotic) optimality.
However, sub-optimal draws turn out not be the dominant terms in the regret, both in our upper bounds and in practice, thus a promising future work is to identify some notion of \emph{minimal number of collisions}, like a recent work \cite{wang2019distributed} studied the minimal amount of communication needed to achieve logarithmic regret, in a similar model that authorizes direct communications between players.
% Similarly to what was done very recently in \cite{wang2019distributed} for the communications between players who collaborate with each other, it would be interesting to characterize the number of collisions needed to achieve logarithmic regret.

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Chapter~\ref{chapter:6}}.}

We believe that our new proof technique of Chapter~\ref{chapter:6} could be used to analyze \GLRklUCB{} under less stringent assumptions than the one made in this chapter (and in previous works), that would require only a few ``meaningful'' changes to be detected.
This promising research direction is left for future work,  but the hope is that the regret would be expressed in term of this number of meaningful changes instead of the number of break-points $\Upsilon_T$.
We shall also investigate whether actively adaptive approaches can attain a $\cO(\sqrt{\Upsilon_T T})$ regret upper-bound without the knowledge of $\Upsilon_T$.
We also believe that combining change-point \emph{localization} with an efficient change-point detection algorithm, such as \GLRklUCB, could lead to an interesting class of more efficient algorithms, as suggested by \cite{Maillard2018GLR}.
